% !TEX root = ../SystemTemplate.tex


\chapter{Project Overview}
This section provides information about the team members, team member roles, project management approach and phase overview.



\section{Team Members and Roles}
Team members are Hannah Aker, in the role of Scrum Master, and Jiasong Yan, in the role of team member.


\section{Project  Management Approach}
The project will be managed using an Agile approach.  There will be 6 sprints total in this project, each lasting 3 weeks. The project backlog is owned by the team, and located on the team Github repository. All parties have access to the Sprint and Product Backlogs. Github issues will be used to track sprint tasks, bugs or trouble tickets, and user stories. The github repository is located at: \url{https://github.com/SDSMT-CSC464-F15/crowdscience} 

\section{Phase  Overview}
This project will be implemented in two phases. The first phase will entail analyzing the Landscape Change Mapper project and adapting a copy of the project for expansion into a generic Crowd Science Mapper. The  second phase will entail adding the necessary freatures to the base project from phase one to create a proof of concept website.

Within phase one, we will implement and then test the adapted Landscape Change Mapper features we add to the project. Delivery is incorporated into the testing phase, because all testing will be done on the live server. Phase two will consist of all the steps in phase one, but will also include a design phase where we fully design the new features to be added.

\section{Terminology and Acronyms}
\begin{itemize}
\item SGT: Stinger Ghaffarian Technologies
\item LCM: Landscape Change Mapper
\item HTML: Hyper-Text Markup Language
\item CSS: Cascading Style Sheet
\item PHP: Hypertext Preprocessor
\end{itemize}