% !TEX root = DesignDocument.tex


\chapter{Future Work}
These are suggestions for future work on the project.
\begin{itemize}
\item Adjust image carousel photo alignment so photos are centred in carousel.
\item Add user profile viewing. Profile may include user information, such as name and user type, as well as recently submitted events and the event sets the user has contributed to.
\item Adjust image loading speed in image carousel, or stored image size, so large images are not visibly loading.
\item Maintain form data on report and register page if user refreshes the page, so user doesn't have to re-enter information.
\item Allow users to query and search event sets to find specific events that meet certain criteria.
\item Allow users to select, display, query, and search multiple event sets.
\item Create a user interface for administrators to create and edit event sets.
\item Create an interface to allow for events to be moderated or flagged as unusual.
\item Create interface for administrator to export and import event sets.
\item Create mobile application or mobile website layout of project.
\item Allow administrator to specify a required field in an event report.
\item Customize image requirements and handling in report. Allow administrator to require a picture is uploaded with event, require the exact location of each image uploaded, require a separate description of each image, etc.
\item Allow the administrator to customize the look and feel of the website when a certain event set is selected.
\item Provide an interface for the user to request their username and password if the user has forgotten their username or password.
\item Provide password encryption before the password is transmitted and stored in the database.
\item Allow administrator to customize the event details that are shown in the table, on the map, or in the individual event page.
\item Add links to the image carousel so that the map can zoom to an event, be taken to the individual event page, or highlight the event report in the table when the image in the image carousel is clicked.
\item When a pin is clicked on in the map, highlight the associated row in the table.
\item When a row in the table is clicked on, highlight the marker for that event on the map.
\item Create a tool-kit or API for administrators to use on other websites or in applications.
\item Create a link to the reporting user's profile where the user's name appears in event reports.
\item Display first name and last name for event author when names are available, and their username otherwise.
\end{itemize}