% !TEX root = sprints_wrapper.tex

This report will cover the backlog items completed in Sprint 4, the current prototype's features, and client communication summaries. 

 \subsection{Backlog Completed}
\begin{itemize}
\item Documentation: revise requirements, project overview, sprint plan, deliverables, and team information
\item Add sample event reports and sample event set data to database (There will be a collection (similar to a table in relational databases) for each event set, one for information about the event set (such as field name, type, restrictions, and maybe even background color/image), and one for user login information) 
\item Implement a select box to choose a different event set, and verify that the connection to the database is working as expected.
\end{itemize}
 
 \subsection{Prototype Features}
 Expanded register screen to include several new fields: email, first name, last name, role, and city, state, and country.  Added selection box for selecting an event set to view. The selection box references a newly created collection in the database, Event Set Information (eventsetsinfo), which contains information about the event report collections in the database. Added sample event report collections to database: Landscape Changes (landscapechange), Bird Sightings (bird), and Wildflower Sightings (wildflower).


\subsection{Client Communication}
\begin{itemize}
\item 1/20/2016: Met with Dr. Qiao to discuss deliverable revisions and backlog revisions, listed below.
\item 1/22/2016: Sent email with revised deliverables and sprint schedule to clients.
\end{itemize}

\subsection{Revised Deliverables}
Already implemented are login and register features.
The minimum viable product includes functionality to select a set of event reports (like birds, butterflies, etc.); and an event reporting interface and map and list event report display whose values and fields update/change to match the currently selected set of event reports.
There will be a section in the design document about additional features that could be implemented in a continuation of the project. This section will include an overview of administrative features (such as a user interface for creating and modifying a set of event reports, and moderating submitted reports) and additional tools for viewing event reports (like sorting, filtering, and searching reports). 

\subsection{Sprint 5 Backlog}
\begin{itemize}
\item Outstanding Documentation: prototype sections, design and testing section for login/register, and start design section for set selection/list
\item Documentation: design and testing section for set selection/list, start design section for report and map
\item Implement reporting interface
\item Implement event report list
\item Implement map interface
\end{itemize}

\subsection{Sprint 6 Backlog}
\begin{itemize}
\item Finish Documentation: design and testing for report and map features, finalize sprint prototype and sprint report sections
\item Final testing (and debugging)
\item Polish prototype
\item Design Fair preparation
\end{itemize}

\subsection{Sprint 4 Successes/Issues}
Jiasong Yan was removed from the project, and necessary revisions to project scope, deliverables and backlog were made. Further details regarding project revision in accordance with Jiasong's removal can be found in the design document.