% !TEX root = sprints_wrapper.tex

This report will cover the backlog items completed in Sprint 5, the current prototype's features, and client communication summaries. 

 \subsection{Backlog Completed}
\begin{itemize}
\item Implemented reporting interface. 
\item Implemented event report table. 
\item Implemented map interface.
\item Implemented single event viewing.  
\item Implemented event image carousel.
\end{itemize}
 
\subsection{Prototype Features}
The following features were added to the prototype:
\begin{itemize}
\item Reporting interface in a separate page: The reporting interface will contain fields specific to the event set selected, in addition to a map for selecting the location of the event and a photo upload interface.
\item Event report table on main page: The table contains event details specific to the event set selected and username for the person submitting the event, as well as links to view all details of the event on a separate page, and to center the map on that event marker. 
\item Event reports map on main page: The map contains markers for all events in the event set. Clicking on a maker on the map will pop-up a bubble with event details, specific to the event set selected, which can be clicked on to navigate to all event details.
\item Single event viewing in a separate page: Clicking on the link icon associated with an event in the event table or on the event pop-up on the map will take the user to a separate page will all details regarding the event.
\item Event image carousel on main page: The carousel will move through the first photo associated with each event set.
\end{itemize}

\subsection{Sprint 6 Backlog}
\begin{itemize}
\item Outstanding Documentation: prototype section for Sprint 5, design/testing section for login/register, design/testing section for set selection/list, design/testing section for set selection/list,start design section for report and map
\item Finish Documentation: finish design/testing for report and map features, finalize sprint prototype and sprint report sections
\item Final testing (and debugging)
\item Design Fair preparation
\end{itemize}

\subsection{Sprint 5 Successes/Issues}
The sprint was an overall success.  The prototype is essentially finished, no major changes should be needed. Documentation fell behind this sprint, additional effort will be put in between sprints 5 and 6 to catch up the documentation with where the prototype is at.