% !TEX root = SystemTemplate.tex
\chapter{User Stories, Backlog and Requirements}
\section{Overview}

This document contains project details for the Crowd Science Mapper project. The Crowd Science Mapper will be a generic crowdsourcing system framework and toolkits, which can be customized by ordinary users with no programming experience using graphical user interface

\subsection{Scope}

This section contain stakeholder information, initial user stories, requirements, and proof of concept results

\subsection{Purpose of the System}
The purpose of this system is to provide a generic crowdsourcing toolkit. That is, to allow ordinary to report and view events, and allow administrators to approve and modify event sets.

\section{ Stakeholder Information}

Stakeholders for this project are academics and researchers who would eventually be the users of this project.

\subsection{Customer or End User (Product Owner)}

Product owners are Dr. Mengyu Qiao and Gail Schmidt, who will assist in the project in mentor roles. As needed, they will assist with prioritizing the product backlog, and identify important features.

\subsection{Developers --Testers}
Developers and testers are Jiasong Yan and Hannah Aker.

\section{Requirements and Design Constraints}

This project will be a HTML based webpage using Java Script to connect to a Mongo database, and hosted on an Apache server

\subsection{System  Requirements}
Webpage should be able to run on all operating systems. This project is not required to have mobile functionality.


\subsection{Network Requirements}
This project will be server based, hosted on an Apache 2.0 server, access supplied to us by Gail Schmidt. 

\subsection{Development Environment Requirements}
Development will be done in HTML, PhP and Java Script. The project will connect to a Mongo database.

\subsection{Project  Management Methodology}
\begin{itemize}
\item Github issues will be used to keep track of backlog and sprint status.
\item All parties have access to the Sprint and Product Backlogs.
\item There will be 6 sprints total in this project.
\item Sprint cycles will last 3 weeks.
\item Source control will be Github.
\end{itemize}

\section{User Stories}

\subsection{User Story \#1}
As a user, I want all the core functionality of the landscape change mapper to be maintained. These functions include, but are not limited to:
\begin{itemize}
\item Visual map representation of events
\item Detailed event list
\item Event reporting interface
\item New user registration
\item User login
\end{itemize}

\subsection{User Story \#2} 
As an administrator, I want to be able to customize a set of events to fit my needs. This may include user input and display items, database design, digital map, webpage color and style, logo, etc. 

\subsection{User Story \#3} 
As an administrator, I want to be able to edit existing event reports.

\subsection{User Story \#4} 
As a user, I want to be able to select which set of events I would like to view.

\section{Supporting Material}
Project Description Document

